Blum axioms and nondeterministic computation of functions

### 2015-12-16 paper.tex
paper.tex: Add Goldreich's definition.

\subsection{Oded Goldreich definition}
\subsection{Krentel's $\OptP$ class}
\subsection{Valiant's $\#\P$ class}
\subsection{Alternative approaches for nondeterministic functions}

>>>>

\subsection{Oded Goldreich definition}

\begin{definition}[Goldreich's definition]
    Let $\bot$ be some special symbol not in $\{0, 1\}^*$.
    (This symbol will represents ``don't know'')
    A nondeterministic machine $M$ computes the function $f$ if,
    when processing the input $x$,
    both the following conditions hold \cite[p.~168]{Goldreich2008}:
    \begin{itemize}
        \item Every branch of $M$ halts
            and outputs either $f(x)$ or $\bot$.
        \item At least one branch of $M$ halts with $f(x)$ on the tape.
    \end{itemize}
\end{definition}

The extra symbol $\bot$ sidesteps the possibility of a branch looping forever.
Now,
every branch is required to halt for the value of the function be defined.
Thus,
we can convert a nondeterministic Turing machine to a deterministic machine
that compute the same function,
albeit with an exponential slowdown
--- the deterministic machine just need to simulate all branches until completion,
to actually be sure every branch halts.

This allows us to comply with the requirements to being an acceptable Gödel numbering:
\begin{itemize}
    \item Any deterministic machine can be understood as a nondeterministic machine
        with a single branch,
        so every computable function appears in the corresponding numbering.
        Thus, the numbering is surjective --- it enumerates every computable function.
    \item Any nondeterministic machine can be simulated by some deterministic machine,
        so the enumeration codomain is the set of computable functions.
    \item This conversion can be done mechanically,
        so we can use the same universal machine and $\sigma$ function
        of the standard Gödel numbering $\pi$
        to comply with the universal machine theorem and the $S_{mn}$ theorem.
\end{itemize}

\subsection{Krentel's $\OptP$ class}
\subsection{Valiant's $\#\P$ class}
\subsection{Alternative approaches for nondeterministic functions}
